\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-09 papers/itsc_2012/final.tex
optimizing agent creation

@@

@@

This paper has presented AORTA, a new city-scale traffic simulation framework
that focuses on ease-of-use and policy configurability. In conjunction with Open
Street Maps, AORTA allows researchers to repeat an experiment in any number of
places with minimal effort. Future work will exploit the flexible infrastructure
of interactions between agent behaviors and intersections by exploring dynamic
replanning and adaptable signal timings. On top of these structures,
applications could experiment with dynamic contra-flow \cite{ITSC11-hausknecht}
and micro-tolling \commentd{Dr. Stone, should we just not mention this yet since
it's not well-published?}. There will also be an effort to improve AORTA as a
framework by including a lane-changing model and preventing gridlock.
\commentm{Perhaps mention concurency plans (with TACC) to simulate arbitrarily large maps?}

@@

\commentd{Er, these don't look like they're alphabetically sorted.}

>>>>

% just draw differences between us and them

@@

mention all the fixed nuances, like pause time at stop sign

  stop sign: FCFS, judged by stopping for the right time within the right dist of
  the end of the intersection.

  traffic signal: duration matters, turns grouped together, how timings are
  propagated.

  autonomous reservation: the greedy approach is a bit wretched. either time
  out, or somehow count how many people are on lanes in the queued groups.
  ideally we'd even recurse and factor in

@@

This paper has presented AORTA, a new city-scale traffic simulation framework
that focuses on ease-of-use and policy configurability. In conjunction with Open
Street Maps, AORTA allows researchers to repeat an experiment in any number of
places with minimal effort. Future work will exploit the flexible infrastructure
of interactions between agent behaviors and intersections by exploring dynamic
replanning and adaptable signal timings. On top of these structures,
applications could experiment with dynamic contra-flow \cite{ITSC11-hausknecht}
or intelligent routing that avoids stopping. There will also be an effort to
improve AORTA as a framework by including a lane-changing model and preventing
gridlock. \commentm{Perhaps mention concurency plans (with TACC) to simulate
arbitrarily large maps?}

@@

\commentd{Er, these don't look like they're alphabetically sorted. And why is
the Google Maps entry so stretched?}
